aircore

### 2024-08-26 examples/aircore.Rmd
add aircore examples and articles

---
title: "aircraft-flask"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aircraft-pfp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

obs <- "/media/sergio/ext5/obspack/obspack_ch4_1_GLOBALVIEWplus_v6.0_2023-12-01/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

@@

```{r readnc, eval = T}
datasetid <- "aircraft-flask"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = FALSE,
                  verbose = T)

@@

```{r checkcols, eval = T}
df[, c("altitude", "altitude_final", "intake_height", "elevation")]
```

@@

```{r aggregatingdata, eval = T}
df2 <- obs_agg(df, cols =  c("year",
                             "month",
                             "day",
                             "hour",
                             "minute",
                             "second",
                             "time",
                             "time_decimal",
                             "value",
                             "latitude",
                             "longitude",
                             "altitude_final",
                             "elevation",
                             "intake_height",
                             # "gps_altitude",
                             # "pressure",
                             # "pressure_altitude",
                             # "u", "v", "temperature",
                             "type_altitude"))
```
## Add local time

@@

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftflask.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircraftflask.png?raw=true)

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_aircraftflask_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircraftflask_map.png?raw=true)

>>>>

---
title: "aircore"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aircore}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

obs <- "Z:/torf/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

@@

```{r readnc, eval = T}
datasetid <- "aircore"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = FALSE,
                  verbose = T)

@@

```{r checkcols, eval = T}
df[, c("altitude", "altitude_final")]
```

@@

```{r aggregatingdata, eval = T}
df2 <- obs_agg(df, cols =  c("year",
                             "month",
                             "day",
                             "hour",
                             "minute",
                             "second",
                             "time",
                             "time_decimal",
                             "value",
                             "latitude",
                             "longitude",
                             "altitude_final",
                             # "elevation",
                             # "intake_height",
                             # "gps_altitude",
                             # "pressure",
                             # "pressure_altitude",
                             # "u", "v", "temperature",
                             "type_altitude"))
```
## Add local time

@@

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircore.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircore.png?raw=true)

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_aircore_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircore_map.png?raw=true)
